Paper Figures

### 2019-08-21 PaperFigures.Rmd
added in yerkes donors for reference

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(
        label="p.signif", hide.ns = TRUE, size=8,
        label.x=1.3,
        label.y = boxplot.stats(data[,yval])$stats[5]*1.4)+
    coord_cartesian(ylim=c(0, boxplot.stats(data[,yval])$stats[5]*1.5))+
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=8)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", "LTBI\nSM-", "LTBI\nSM+", "TB\nSM-", "TB\nSM+"))+
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(
        comparisons = list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-")),
        label="p.signif", size=8,
        label.y = boxplot.stats(data[,yval])$stats[5]*1.4)+
        coord_cartesian(ylim=c(0, boxplot.stats(data[,yval])$stats[5]*1.5))+
        labs(x="", y="")
}

@@

healthy.cols<- c("SM+" = "#1a9850", "SM-" ="#91cf60")
ltbi.cols<- c("SM+" = "#2166ac", "SM-" = "#85ABD1")
tb.cols<- c("SM+" = "#b2182b", "SM-"="#E59EA6")
all.cols<- c("HC SM+" = "#1a9850", "HC SM-" ="#91cf60",
             "LTBI SM+" = "#2166ac", "LTBI SM-" = "#85ABD1",
             "TB SM+" = "#b2182b", "TB SM-"="#E59EA6")
```

@@

#All groups
Dont worry I can change this so the ns bars don't show up, especially for the cytokines since I have no idea why that giant NS is there. But for now I'm leaving them so we know.
```{r}
cd4<-plot_filter(subset(CD4, CD4$Stim=="UN"))
cyt<-plot_filter(subset(CYT, CYT$Stim=="PMA"))
phen<-plot_filter(subset(PHEN, PHEN$Stim=="PMA"))
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-allplot(melt[melt$variable=="T-bet",], "disease", "value", all.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-allplot(melt[melt$variable=="GATA3",], "disease", "value", all.cols)+    
    facet_wrap(~variable)

c<-allplot(melt[melt$variable=="CXCR3",], "disease", "value", all.cols)+    
    facet_wrap(~variable)

d<-allplot(melt[melt$variable=="CCR4",], "disease", "value", all.cols)+    
    facet_wrap(~variable)

```{r, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-allplot(melt[melt$variable=="IFNg",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-allplot(melt[melt$variable=="TNFa",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-allplot(melt[melt$variable=="IL4",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-allplot(melt[melt$variable=="IL13",], "disease", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

#Healthy Adults
*Is this superfluous now?*  
####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=18, fig.height=9.5}
melt<-melt(cyt, id.vars=c("TB","SM"), measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
baseplot(melt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")+coord_cartesian(ylim=c(0,40))
```

@@

```{r, fig.width=5, fig.height=10}
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

@@

booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="Frequency of Marker+ CD4+ T cells (%)")
```

@@

```{r cytokine, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-baseplot(melt[melt$variable=="IFNg",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-baseplot(melt[melt$variable=="TNFa",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-baseplot(melt[melt$variable=="IL4",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-baseplot(melt[melt$variable=="IL13",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

@@

####Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers, however this does not differ by S. mansoni status
```{r ics main four markers, fig.width=16, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("ifng_T-bet", "ifng_GATA3", "ifng_CXCR3", "ifng_CCR4"))
melt$variable<-gsub("ifng_", "", melt$variable)

a<-baseplot(melt[melt$variable=="T-bet",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-baseplot(melt[melt$variable=="GATA3",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)
c<-baseplot(melt[melt$variable=="CXCR3",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)

d<-baseplot(melt[melt$variable=="CCR4",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=16, fig.height=8}
a<-baseplot(og, "SM", "OG_freq", ltbi.cols)+
    labs(y="Proliferating CD4+ T cells (%)")+coord_cartesian(ylim=c(0,5))
melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))

@@

b<-booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels)+
    labs(y="Cytokine+ Proliferating\nCD4+ T cells (%)")

cowplot::plot_grid(a, b, ncol=2, rel_widths=c(1.5,3.5), align="h")
```

@@

```{r og main four markers, fig.width=16, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable=="T-bet",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")+coord_cartesian(ylim=c(0,100))

b<-baseplot(melt[melt$variable=="GATA3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+coord_cartesian(ylim=c(0,100))

c<-baseplot(melt[melt$variable=="CXCR3",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+coord_cartesian(ylim=c(0,100))

d<-baseplot(melt[melt$variable=="CCR4",], "disease", "value", ltbi.cols)+    
    facet_wrap(~variable)+coord_cartesian(ylim=c(0,100))

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")
```

#TB  
####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*
```{r tb cytokine ics, fig.width=16, fig.height=8}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
og<-filter_tb(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_tb(subset(OGPHEN, OGPHEN$Stim=="PEP"))

#generate cytokine table for graphing
melt<-melt(cyt, 
    id.vars=c("TB","SM"), 
    measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
cyt_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))
#graph cytokine with facets
keep <- baseplot(melt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=cyt_groups)+
    labs(y="Frequency of Cytokine+ \nCD4+ T cells (%)")
```

```{r, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))
cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

a<-baseplot(melt[melt$variable=="IFNg",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="Frequency of Cytokine+ CD4+ T cells (%)")

b<-baseplot(melt[melt$variable=="TNFa",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

c<-baseplot(melt[melt$variable=="IL4",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

d<-baseplot(melt[melt$variable=="IL13",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)

```{r main four markers, fig.width=16, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4"))
melt$variable<-gsub("TH1_", "", melt$variable)

a<-baseplot(melt[melt$variable=="T-bet",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    labs(y="(%) Total CD4+ T cells")

b<-baseplot(melt[melt$variable=="GATA3",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)

c<-baseplot(melt[melt$variable=="CXCR3",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)

d<-baseplot(melt[melt$variable=="CCR4",], "SM", "value", tb.cols)+    
    facet_wrap(~variable)

booleanplot(test, "variable", "value", tb.cols)+facet_wrap(~tf, scales="free", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="Frequency of Transcription Factor \n Mtb-Specific TH1 cells (%)")

>>>>

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    facet_wrap(~variable)+
    scale_x_discrete(labels=c("\nNaive","SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10)+
    labs(x="", y="")
}

cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

@@

healthy.cols<- c("SM+" = "#1a9850", "SM-" ="#91cf60")
ltbi.cols<- c("SM+" = "#2166ac", "SM-" = "#85ABD1")
tb.cols<- c("SM+" = "#b2182b", "SM-"="#E59EA6")
all.cols<- c("Naive" = "#C8D0D8","HC SM+" = "#1a9850", "HC SM-" ="#91cf60",
             "LTBI SM+" = "#2166ac", "LTBI SM-" = "#85ABD1",
             "TB SM+" = "#b2182b", "TB SM-"="#E59EA6")
```

@@

#All groups
Dont worry I can change this so the ns bars don't show up, especially for the cytokines since I have no idea why that giant NS is there. But for now I'm leaving them so we know.
```{r}
cd4<-filter_all(subset(CD4, CD4$Stim=="UN"))
cyt<-filter_all(subset(CYT, CYT$Stim=="PMA"))
phen<-filter_all(subset(PHEN, PHEN$Stim=="PMA"))
og<-filter_all(subset(OG, OG$Stim=="SEB"))
ogphen<-filter_all(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, fig.width=20, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))

allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))

allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, scales="free", labeller = cyt_groups, ncol=4)+
    labs(y="(%) Total CD4+ T cells")+
    theme(legend.position="bottom") 
```

#Healthy Adults
*Is this superfluous now?*  
####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=18, fig.height=9.5}
melt<-melt(subset(CYT, CYT$Stim=="PMA"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) CD4+ T cells")+coord_cartesian(ylim=c(0,45))

cyt<-filter_ltbi(melt)
b<-baseplot(cyt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,45))

cyt<-filter_tb(melt)
c<-baseplot(cyt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,45))

cowplot::plot_grid(a, b, c, ncol=3)
```

@@

```{r, fig.width=16, fig.height=20}
phen<-filter_hc(subset(PHEN, PHEN$Stim=="PMA"))
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

@@

a<-booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells")

phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PMA"))
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

b<-booleanplot(test, "SM","value", ltbi.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))

phen<-filter_tb(subset(PHEN, PHEN$Stim=="PMA"))
test<-melt(phen, id.vars=c("TB", "SM"), 
           measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4",
           "TH2_T-bet", "TH2_GATA3", "TH2_CXCR3", "TH2_CCR4"))

c<-booleanplot(test, "SM","value", tb.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))

cowplot::plot_grid(a, b, c, ncol=3)
```

@@

```{r cytokine, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))

a<-baseplot(melt[melt$variable=="IFNg",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

b<-baseplot(melt[melt$variable=="TNFa",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))

c<-baseplot(melt[melt$variable=="IL4",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y = (.95*.013))+
    coord_cartesian(ylim=c(0,.013))

d<-baseplot(melt[melt$variable=="IL13",], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

####Mtb-specific TH1 cytokine producing cells express both TH1 and TH2 lineage-specific markers, however this does not differ by S. mansoni status
```{r ics main four markers, fig.width=16, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("ifng_T-bet", "ifng_GATA3", "ifng_CXCR3", "ifng_CCR4"))
melt$variable<-gsub("ifng_", "", melt$variable)
melt$variable <- factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

cowplot::plot_grid(a,b,ncol=2)
```

#TB 
```{r, narrow down tb data}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
```
####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*

```{r, fig.width=16, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa", "IL4", "IL13"))

a<-baseplot(melt[melt$variable=="IFNg",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="(%) CD4+ T cells")+
    coord_cartesian(ylim=c(0,.06))

b<-baseplot(melt[melt$variable=="TNFa",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.15))

c<-baseplot(melt[melt$variable=="IL4",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))

d<-baseplot(melt[melt$variable=="IL13",], "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))

@@

```{r main four markers, fig.width=16, fig.height=8}
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_T-bet", "TH1_GATA3", "TH1_CXCR3", "TH1_CCR4"))
melt$variable<-gsub("TH1_", "", melt$variable)
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

cowplot::plot_grid(a, b, ncol=2)
```

booleanplot(test, "variable", "value", tb.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")+
    coord_cartesian(ylim=c(0,55))+
    stat_compare_means(label="p.signif", hide.ns=TRUE, label.y=50, size=10)

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=16, fig.height=8}
a<-baseplot(og, "SM", "OG_freq", ltbi.cols)+
    labs(y="(%) CD4+ T cells")+
    facet_wrap(~TB, labeller = as_labeller(c("LTBI"="Proliferation")))+
    coord_cartesian(ylim=c(0,3))

melt<-melt(ogphen, id.vars=c("TB", "SM"), measure.vars = grep("._._.", names(ogphen)))
test<-melt[-grep("._._._.", melt$variable),]
test<-filter(test, variable!="x_x_x")
test$variable<-factor(test$variable, levels=c(
"T_G_x" ,       
"T_x_x" ,         
"x_G_x" ,         
"T_G_4" ,
"T_x_4" ,         
"x_G_4" ,         
"x_x_4"          
))
test$group<-"TH1/2"
for(i in 1:length(test$group)){
    if(test$variable[i] %in% c("T_G_x", "T_x_x", "x_G_x")){
        test$group[i]<- "TH1"
    }
    else if (test$variable[i] == "x_x_4"){
        test$group[i]<- "TH2"
    }
}

@@

b<-booleanplot(test, "variable", "value", ltbi.cols)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    facet_grid(~group, scales="free_x", space="free_x")+
    labs(y="(%) Proliferating CD4+ T cells")

cowplot::plot_grid(a, b, ncol=2, rel_widths=c(1,3.5), align="h")
```

```{r og main four markers, fig.width=16, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3", "CXCR3", "CCR4"))
melt$variable<-factor(melt$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(label="p.format", size=6, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

cowplot::plot_grid(a,b,ncol=2)
```

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free_x", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
```

@@

@@

booleanplot(test, "variable", "value", ltbi.cols)+facet_wrap(~tf, scales="free", ncol=4)+
    scale_x_discrete(labels = labels, breaks=breaks)+
    stat_compare_means(label="p.signif", hide.ns = TRUE, size=6)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
